This weather station was once used by the druidic elves to help control the weather on the dry side of the mountains.

The halls are lush with foliage and lit with some light even though it is clear that the facility is underground.
There is an earthy smell and occasional sound of trickling water running down the walls.
Small puddles of water dot the floor.


A1: Entrance

Heavy vines cover this entrance, making it difficult to see.
Detect magic will reveal that this door is magical, and identify will reveal that the door can be helping the plants near the entrance grow.
Barring access to identify, a history or arcana check may also reveal how to open the door.
This area links to A2.

A2: Greenhouse

Blooming plants fill this large hemispherical chamber.
Tree trunks were shaped to form benches in a circle around a stone altar in the middle of the room.
Druids or those with reasonable history or religion skills may recognize this as a place to worship nature.
With an investigation of 15+, the party may find natural potions.
This area links to A1 and A3.

A3: Library

The plant growth has not been kind to the relics and texts in this library.
Most of the shelves are rotting away and will fall apart if the party is not too careful.
An investigation will reveal a read book with some sort of animal skin hidden among the ruined relics and texts.
This book contains vivid images of druids changing into more complex shapes of beasts that can swim.
This area links to A2, A4, A5, and A7.

A4: Dining Hall

This dining hall could feed about a dozen people.
The tables and tableware are completely destroyed.
This area links to A6 and A7.

A5: Dorms

As with the dining hall, these dorms have been completely destroyed as the plants have taken over.
Hidden in a footlocker is a Cloak of Elvenkind.
Also, there is a token that helps indicate the location of the hidden doorway to area A8.
This area links to A3 and A7.

A6: Kitchen

This kitchen has the remnants of a cooking pit.
The most important feature in this room is an overgrown goodberry bush.
This area links to A4.

A7: Hidden Door

This hidden door links to area A8.

A8: Weather Control Room

This is a tall chamber with an opening up to the sky, but the room is well preserved.
There are 4 small stone altars, each with a magical stone.
Each stone is rectangular and made of a tan stone.
The stones are marked with the druidic ruins for air, water, fire, and earth.
When the stones are unlocked, they transform into elementals (Air Elemental, Earth Elemental, Fire Elemental, and Water Elemental) and attack.
These elementals may be modified to be an appropriate challenge for party level.
Breaking the stones will reduce the elementals to one third health.
A storm starts overhead.
The elementals are upset for being trapped and used.
Upon investigation, the tables in the room give hints that the facility was used to control the weather.
This area links to A7 and A9.

A9: Catacombs

This area holds the bones of the elven druids that constructed this facility.
Finkas is being held here with the bodies of the adventuring party he was guiding.
There is a Cloaker and an Eladrin guarding Finkas.
This area links to A8.

