If the party chooses to follow-up on the note in the Bandit Captain's pocket, they can receive payment for their own assault, if they can bluff their way through the situation!

The Alehouse is one of a myriad of grungy bars in Camellia.
Party members will be challenged at the door and will have to lie (DC 15) or show their bounty to get in.

Rook (Bandit Captain) can be found at a table in the back of the bar.
The various bargoers look at least as dangerous as the group that came to attack the party, with some members looking more dangerous.

Rook will speak with a few members of the party.
If the party can successfully convince her that they are the bandits that attacked the party, then Rook will pay 35 gp.

Rook has the following knowledge about the attack:

* The job came through some contacts in the thieves guild on the dry side who are looking for the Lost City of Gold.
* These contacts do not want anyone else getting in the way of their operations.
* Rook thinks that the Lost City of Gold is a complete myth.
* The Lost City of Gold was an old mining town that got rich and was taken over by the wild forest.
* Killing is a last resort for thieves in Theaceae, so Rook doubts that this group had anything to do with Finkas Tealeaf going missing.

To get the payment and information from Rook, the party must succeed in a series of skill checks.
The skills must reasonably be related to convincing Rook that the party members are in the thieves guild.
The DC starts at 15.
Each successful check lowers the DC by 1.
Each unsuccessful check increases the DC by 2.

If the DC reaches 20, then Rook will demand that the party leaves.
Others in the bar will come to Rook's defense if the party attacks.
Rook will let the party leave peacefully at any point.
