Session 1 - 31 August 2020
Day 2762

The days were beginning to blur together again, the same as before I stumbled upon Ada.  I can’t recall how long ago that was.  I don’t know what day it is.  It must be late summer.  The days are still warm, but the nights are beginning to chill.  The nights… the nights grow long… the nights…  I have not slept for 2762 of them.  

But, today was different.

Ada and I were gathering supplies to trek over the mountains in search of who knows what, when a flunkie of some local noble asked for volunteers for a lucrative and potentially hazardous task.  An eclectic group of people including myself and Ada offered our services and were given a name, time to meet, and directions to a local inn for the deep of pocket.  Madam Tealouse or Tealeaf or… anyways something like that.

While being left waiting for what seemed like hours, the lot of us got acquainted.  Two monastery folk, Ekdos and some drunkard devil half-breed named Creed.  With a face like that, I would be a drunkard, too.  A local sword named Roland. And, a foreigner with the vaguest of titles for a name… “He who dreams.”  I’ve never seen someone like the Foreigner or the half-breed before.  I’ve read stories about the foreigner’s ancestry. Humaphants? Elemans?  The devil… I don’t know.  Both of them will prove to be interesting specimens studies, alive or dead.

A half-height woman finally graced us with her presence and we were given details on what we were to do and what we would be paid upon completion.  Find her kid, Finkas, who didn’t show up as expected in Wolf Point six months ago.  Took a bunch of people with too much time and money on their hands to find some lost city of gold.  It is doubtful our expedition will produce anything more than weathered bones, but I won’t complain about the extra coin on the other side.

Later, we found out the hard way that an anonymous somebody hired a bunch of thugs through a third party to give us trouble.  Rook didn’t really hire the best people money could buy and that cost some people their lives tonight.  A minor show of force was enough for her to spill the beans about some unknown contact on the other side of the mountain wanting to disrupt any attempt to recover the half-height kid.

Tomorrow, just after sunrise, we leave this forsaken town.  Tomorrow, I get even further away from the hunters.  Tomorrow… 
