7 September 2020

**Day 2763**


We are finally on our way.  We spent the morning hours setting in motion the local constabulary to dismantle Rook’s enterprise.  With any luck, we will not return here and find ourselves in need of someone with her connections

When we arrived at the caravan, the Foreigner was making friends with the beasts of burden.  We would have appreciated the opportunity to observe and record the interaction, but Abigail began sniffing around and ruined the moment.

The Devil finally arrived, complaining and half inebriated.  And Ada showed up on time.  Frankly, we are surprised she was not late from giving a passing denizen a lecture on the historical and archeological significance of the different rocks she found lying in the street.


**Day 2770**


After a week of relatively uneventful travel, (except for the Foreigner and the goats engaging in ritualistic displays of virility), the caravan stopped for the night near the ruins of an ancient and abandoned elvish metropolis lost to time in the upper altitudes of the mountain pass.  We remember Ada speaking of this place.  Deserted for a millenia?  We cannot help but feel like we have been here before, but we are certain our feet have never touched this soil before today.  Still...

image:: /images/hwdHeadButtsTx.png


The twilight silence of the night was shattered by several apparitions, likely of the former residents, appeared and siphoned the life from one of the guards.  A guard who decided to abandon their post to go digging about in the ruins.  They were lucky and not.  Once the undead were dispatched, Ada did whatever she does and found an ancient sword near the guard’s corpse.  The caravan leader is convinced the apparitions are the long dead come to retrieve what is rightfully theirs.

Ada did not need convincing to go return the sword.  She was overly eager to have dedicated time to explore the ruins and, as usual, went running off by herself.  The foreigner was amicable to the idea of returning the possessions of the dead.  The Devil required significant cajoling to overcome his inescapable bemoaning of wounds incurred from the encounter with apparitions.

We discovered where the errant guard travelled and avoided at least one trap by watching a pillar collapse upon the Foreigner.  We are fairly certain this was a result of clumsiness, but the Foreigner claims it was a trap and there were more to be found.  Upon discovering an armory patrolled by a phantom that made the creatures from before seem insignificant, it was my hope that Ada would return the sword and we would be safely on our way.  We should have known not to expect this level of rationality from Ada when ancient artifacts are involved.  There was also the matter of the Devil taking it upon himself to assail the immense creature for no apparent reason.  Fortunately, the being only wanted its sword returned and, after an ill-fated attempt to deceive the phantom, and two barely conscious people, we were able to remove ourselves from danger.

During this evening’s events, there were two curious incidents with the Foreigner.  With the apparitions, he dissolved into an animated puddle of goo.  With the phantom in the ruins, the Foreigner reconstituted himself into some strange beast made of stone.  Both times, after the altercations were resolved, the sleeping Foreigner’s body returned to where the creatures once were.  He claims to have fallen asleep and experienced strange dreams that, upon further interrogation, correlate with the events that occurred when the strange creatures were present.  These episodes warrant further observation and investigation.  Maybe this is where his moniker comes from?

Then, there is the matter of this “coin” we found among the grave robbers.  It reminds me of markings on the bounty issued by Rook... We shall bring this up to the group once they have recovered in the morning.

