Session 3 - 14 September 2020

**Day 2787**

We finally arrived in wolf point after another week of inane walking through McKinley Pass.  The outpost town is smaller and greener than expected. The others quickly acquired lodging from the innkeeper, Balris Grirlei, an interesting specimen of elvish descent with very little hair where he should and very much where he should not have it.  The product of the elf’s cooking isn’t unpalatable, however, his ingredients leave a lot to be desired, chiefly the use of a goat found dead and drained of all of its blood.  We did not have the presence of mind the moment, but we must inquire further in regards to this sanguine phenomenon.

Prior to the odd dinner, the other members of the search party and ourselves queried the local inhabitants, including one Tirza Wolff, the chief proprietor of the Wolff Trading Post.  We acquired a couple of days worth of rations and a crudely detailed map which has the potential, as limited as it may be, to help discover the remains of Finkas. Then we visited the local goat herder, Lukas Bauer, and his interesting establishment engaged in the husbandry, rearing, and proffering of animals not dissimilar from the beasts of burden that ferried us over the mountain.

Collectively, we learned the following:

Finkas’s departed Wolf’s Point approximately six months ago

There were four male and three female humanoids green to exploration, and four goats from the goat herder, in addition to Finkas and his personal animal

The group secured approximately three months of supplies for what was supposed to be at most three months total of out and back travel and exploration of undetermined location within nearby fey forest rumored to possess the following characteristics:

  Berries that induce an addiction response upon first consumption
  A closed weather system independent of regional meteorological events
  An altered flow of time, 
  A city of gold, possibly the target of their expedition
  A mortality rate near to, if not, 100% for anyone who enters its confines

before leaving the would be explorers commissioned a local smith to craft tray like objects with irregular and unusual edges

Then there is the matter of the “Friends.”  We have not dealt with their ilk since Douro and they did not take overt notice of us then.  The coin we found in the mountain ruins is some sort of mark of association with the criminal organization.Judging by Wolff and Bauer visibly balking when asked about the coin, The Friends presence is not a welcome one in Wolff Point.  We tried to badger the others to commit to a show of force, but they did not acquiesce and would rather wait for the wolves to come knocking.  And then, a note under Ada’s door.  An invitation to do business.
