Session 4 - 21 September 2020

**Day 2788**

We are finally on our way out of Wolff Point.  One night was one night too many in that place.  At least we are leaving of our own accord instead of the usual.  The innkeeper has agreed to look after some of my gear for a small fee and is willing to keep any future mysterious, blood drained corpses away from the butcher until we get back.


**Day 2795**

Seven tedious, stodgy, trite and monotonous days on a lightly wooded road brought us to the fork where the target otherworldly forest allegedly begins.  There were no discernable demarcations to be found, and who knows when we actually entered the woods.  Half way through the night a trio of half humanoid half goat creatures approached us in out-of-place merriment, inviting us to a party.  We were not fond of the idea, but if there are intelligent creatures there, it may reduce the time required to find what remains of Finkas.  We spoke with one of the Satyrs who goes by the moniker Veq.  They seemed very agitated when asked what their proper name is.  We will try to remember this for future interactions.

The party contained numerous species of seemingly intelligent life that we are unfamiliar with.  There are several flavors of sprite or pixie type creatures.  Several novel subspecies of elves we have never seen or heard of from Ada or previous encounters.  Maybe they are one species with highly varied skin tones.  It seems unlikely to have for distinct species so close together.  More Satyrs or fauns were present, what I think are wood spirits, or dryads? And several specimens of dwarf-like creatures, but smaller. Some appearing quite jovial with their visages beset by hair, and others appearing twisted and menacing with oddly damp red hats.  It reminds us of blood.


**Day 2795**

The others gathered around an elf who claimed to have knowledge of the whereabouts of Finkas.  The foreigner, the ever calm Ekdos, and Ada were oddly eager to follow.  Assenting to their desires landed us in some sort of prison built into the root ball of a giant tree with  insufferable legal representation provided by…?  Ada may or may not have sold a bill of goods to the barrister with all of our names on it, but only her signature.  And then ... nothing.
